\pkg{Rgbp}: Bayesian Hierarchical Modeling and Frequentist Method Check

### 2013-04-17 jss/article.tex
correction

Next, we will check whether the estimated coverage probabilities are at least 95\% varying the true shrinkage values. Note that, if we want to check a coverage probability under the different parameter values, $r$ and $\beta$, for example 150 for $r$ and $(-1, 0.5)^{T}$ for $\beta$, the appropriate code is \code{R> coverage(b, A.or.r = 150, reg.coef = c(-1, 0.5), covariates = x, nsim = 10000)}. Using this adjustment option, we drew Rao-Blackwellized coverage estimates varying true shrinkage values from 0.01 to 0.99, fixing $\beta$ as estimated values.
\begin{CodeChunk}
\begin{CodeInput}
R> shr <- seq(0.01, 0.99, by = 0.05)
R> r.trial <- mean(n) * shr / (1 - shr)
R> cov.save <- sapply (1 : length(r.trial), function(i){
R>               coverage(b, A.or.r = r.trial[i], reg.coef = c(-1.194, 0.389), 
R>                        covariates = x1, nsim = 500)$average.coverageRB
R>             })
R> plot(shr, cov.save, type = "l", ylim = c(0.8, 1), xlab = "Shrinkage",
R>      ylab ="", main = "Rao-Blackwellized Coverage Estimate", lwd = 3,
R>      col = 2)
R> abline(h = 0.95)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 5.5cm]{baseball4.png}
\end{center}
\end{figure}

>>>>

Next, we will check whether the estimated coverage probabilities are at least 95\% varying the true shrinkage values. Note that, if we want to check a coverage probability under the different parameter values, $r$ and $\beta$, for example 150 for $r$ and $(-1, 0.5)^{T}$ for $\beta$, the appropriate code is \code{R> coverage(b, A.or.r = 150, reg.coef = c(-1, 0.5), covariates = x, nsim = 10000)}. Using this adjustment option, we drew Rao-Blackwellized coverage estimates varying true shrinkage values from 0.01 to 0.99, fixing $\beta$ as estimated values.
\\

\begin{CodeChunk}
\begin{CodeInput}
R> shr <- seq(0.01, 0.99, length.out = 20)
R> r.trial <- mean(n) * shr / (1 - shr)
R> cov.save <- sapply (1 : length(r.trial), function(i){
R>               coverage(b, A.or.r = r.trial[i], reg.coef = c(-1.194, 0.389), 
R>                        covariates = x1, nsim = 500)$average.coverageRB
R>             })
R> plot(shr, cov.save, type = "l", ylim = c(0.8, 1), xlab = "Shrinkage",
R>      ylab ="", main = "Rao-Blackwellized Coverage Estimate", lwd = 3,
R>      col = 2)
R> abline(h = 0.95)
\end{CodeInput}
\end{CodeChunk}
\begin{figure}[h]
\begin{center}
\includegraphics[width = 5.5cm]{baseball4.png}
\end{center}
\end{figure}
